The Shape and Color of Politics

### 2023-09-18 chapter_2/src/slides/slides 2.qmd
think I missed some files on last pr

---
title: "The Shape and Color of Politics"
author:
  - name: Damon C. Roberts [{{< fa brands orcid size=xs >}}](https://orcid.org/0000-0002-4360-3675)
format:
  revealjs: 
    embed-resources: true
    theme: [dark, ../assets/slides/custom.scss]
    transition: slide
    scrollable: true
    incremental: true
    slide-number: true
    toc: true
    toc-depth: 2
    slide-level: 5
    bibliography: ../../assets/references.bib   
    self-contained: true
    output-file: color_and_conversation.html
execute:
  echo: false
---

```{r}
#| label: setup-block
# Set seed
set.seed(12102023)
# Load libraries
box::use(
  ggplot2[
    ggplot
    , aes
    , geom_density
    , theme_minimal
    , geom_vline
  ]
  , modelsummary[
    datasummary_skim
    , datasummary_balance
    , modelsummary
  ]
  , ./R/predicted_prob_bar[...]
  , data.table[...]
)

# Execute the cleaning script
source("./eda/study_1/cleaning.R")
# Load cleaned data
list_df <- list()
list_df[["cleaned"]] <- read.csv(
  file = "../data/clean/cleaned_pavlovia.csv"
)
# Load fitted models
load("../data/temp/models/study_1_fitted.RData")
```

@@

[![1860s Ballots](../assets/slides/imgs/ballots.avif){#fig-ballots}](https://slate.com/news-and-politics/2020/02/ballot-history-photo-essay.html)

@@

[![Democratic National Convention](../assets/slides/imgs/1980_dem_convention.jpg){#fig-1980-dem height=100}](https://untappedcities.com/2021/08/12/1980-democratic-national-convention/)

[![Republican National Convention](../assets/slides/imgs/1980_rep_convention.jpg){#fig-1980-rep height=100}](https://reuther.wayne.edu/node/9207)

@@

[![2000 Presidential Election map](../assets/slides/imgs/2000_election_map.webp){#fig-2000-election-map width=200}](https://www.google.com/url?sa=i&url=https%3A%2F%2Fwww.smithsonianmag.com%2Fhistory%2Fwhen-republicans-were-blue-and-democrats-were-red-104176297%2F&psig=AOvVaw3mlqWWKalyCl0gzVJDCIV5&ust=1694829600914000&source=images&cd=vfe&opi=89978449&ved=0CA8QjRxqFwoTCJCNg7bCq4EDFQAAAAAdAAAAABAT)

@@

![Republicans pre-2000](./assets/img/rnc_logo_pre-2000.png){#fig-republican}

![Democrats pre-2000](./assets/img/dnc_logo_1960.png){#fig-democrat}

![Republicans 2023](./assets/img/rnc_logo_2023.png){#fig-republican-post}

![Democrats 2023](./assets/img/dnc_logo_2023.png){#fig-democrat-post}

@@

[![The public](../assets/slides/imgs/division.webp){#fig-public}](https://www.brookings.edu/articles/what-is-a-brokered-convention-what-is-a-contested-convention/)

@@

```{mermaid}
%%| label: fig-zaller
%%| fig-cap: Memory model of info processing
graph TD;
A[Sampled pre-existing info] -->|Stronger impacts when less pre-existing knowledge| C[Updated attitudes]
B[New info] --> C
```

@@

```{mermaid}
%%| label: fig-online-model
%%| fig-cap: Online model of info processing
graph TD;
A[Pre-existing beliefs] --> C[Updated beliefs]
B[New information] -->|If it aligns with current beliefs| C
```

@@

{{< include ../../assets/_theory.qmd >}}

@@

![Red condition](./study_1/assets/rep_yard_sign_round_1.png)
![Blue condition](./study_1/assets/dem_yard_sign_round_1.png)
![White condition](./study_1/assets/cont_yard_sign_round_1.png)

@@

![Red condition](./study_1/assets/rep_yard_sign_round_2.png)
![Blue condition](./study_1/assets/dem_yard_sign_round_2.png)
![White condition](./study_1/assets/cont_yard_sign_round_2_3.png)

@@

![Red condition](./study_1/assets/rep_yard_sign_round_3.png)
![Blue condition](./study_1/assets/dem_yard_sign_round_3.png)
![White condition](./study_1/assets/cont_yard_sign_round_2_3.png)

@@

![Example of treatment](../assets/slides/imgs/treatment.gif){#fig-treatment-example}

@@

from sys import path # for path management
from cv2 import imread, imwrite # for color detection
    #* user-defined
#path.append("../")
from PY.helper import colorDetector

@@

# Load gop image to read
img = imread("./assets/img/gop_2022.png")

@@

transformed= imwrite("../data/temp/study_2/gop_2022_transformed.png", img_transformed) # save transformed image

masked= imwrite("../data/temp/study_2/gop_2022_detected.png", result) # save masked image
```

::: {#fig-color-detection-example layout-ncol="2"}
![Resized original image](../data/temp/study_2/gop_2022_transformed.png){#fig-resized}

![Masked](../data/temp/study_2/gop_2022_detected.png){#fig-masked}

>>>>

---
title: "The Shape and Color of Politics"
author:
  - name: Damon C. Roberts [{{< fa brands orcid size=xs >}}](https://orcid.org/0000-0002-4360-3675)
format:
  revealjs: 
    embed-resources: true
    theme: [dark, ../../assets/slides/custom.scss]
    transition: slide
    scrollable: true
    incremental: true
    slide-number: true
    toc: true
    toc-depth: 2
    slide-level: 5
    bibliography: ../../../assets/references.bib   
    self-contained: true
    output-file: color-book.html
execute:
  echo: false
---

```{r}
#| label: setup-block
# Set seed
set.seed(12102023)
# Load libraries
box::use(
  ggplot2[
    ggplot
    , aes
    , geom_density
    , theme_minimal
    , geom_vline
  ]
  , modelsummary[
    datasummary_skim
    , datasummary_balance
    , modelsummary
  ]
  , ../R/predicted_prob_bar[...]
  , data.table[...]
)

# Load cleaned data
list_df <- list()
list_df[["cleaned"]] <- read.csv(
  file = "../../data/clean/cleaned_pavlovia.csv"
)
# Load fitted models
load("../../data/temp/models/study_1_fitted.RData")
```

@@

[![1860s Ballots](../../assets/slides/imgs/ballots.avif){#fig-ballots}](https://slate.com/news-and-politics/2020/02/ballot-history-photo-essay.html)

@@

[![Democratic National Convention](../../assets/slides/imgs/1980_dem_convention.jpg){#fig-1980-dem height=100}](https://untappedcities.com/2021/08/12/1980-democratic-national-convention/)

[![Republican National Convention](../../assets/slides/imgs/1980_rep_convention.jpg){#fig-1980-rep height=100}](https://reuther.wayne.edu/node/9207)

@@

[![2000 Presidential Election map](../../assets/slides/imgs/2000_election_map.webp){#fig-2000-election-map width=200}](https://www.google.com/url?sa=i&url=https%3A%2F%2Fwww.smithsonianmag.com%2Fhistory%2Fwhen-republicans-were-blue-and-democrats-were-red-104176297%2F&psig=AOvVaw3mlqWWKalyCl0gzVJDCIV5&ust=1694829600914000&source=images&cd=vfe&opi=89978449&ved=0CA8QjRxqFwoTCJCNg7bCq4EDFQAAAAAdAAAAABAT)

@@

![Republicans pre-2000](../assets/img/rnc_logo_pre-2000.png){#fig-republican}

![Democrats pre-2000](../assets/img/dnc_logo_1960.png){#fig-democrat}

![Republicans 2023](../assets/img/rnc_logo_2023.png){#fig-republican-post}

![Democrats 2023](../assets/img/dnc_logo_2023.png){#fig-democrat-post}

@@

[![The public](../../assets/slides/imgs/division.webp){#fig-public}](https://www.brookings.edu/articles/what-is-a-brokered-convention-what-is-a-contested-convention/)

@@

```{mermaid}
%%| label: fig-zaller
%%| fig-cap: Memory model of info processing
%%| fig-width: 6.5
graph TD;
A[Sampled pre-existing info] -->|Stronger impacts when less pre-existing knowledge| C[Updated attitudes]
B[New info] --> C
```

@@

```{mermaid}
%%| label: fig-online-model
%%| fig-cap: Online model of info processing
%%| fig-width: 6.5
graph TD;
A[Pre-existing beliefs] --> C[Updated beliefs]
B[New information] -->|If it aligns with current beliefs| C
```

@@

{{< include ../../../assets/_theory.qmd >}}

@@

![Red condition](../study_1/assets/rep_yard_sign_round_1.png)
![Blue condition](../study_1/assets/dem_yard_sign_round_1.png)
![White condition](../study_1/assets/cont_yard_sign_round_1.png)

@@

![Red condition](../study_1/assets/rep_yard_sign_round_2.png)
![Blue condition](../study_1/assets/dem_yard_sign_round_2.png)
![White condition](../study_1/assets/cont_yard_sign_round_2_3.png)

@@

![Red condition](../study_1/assets/rep_yard_sign_round_3.png)
![Blue condition](../study_1/assets/dem_yard_sign_round_3.png)
![White condition](../study_1/assets/cont_yard_sign_round_2_3.png)

@@

![Example of treatment](../../assets/slides/imgs/treatment.gif){#fig-treatment-example}

@@

from sys import path # for path management
from cv2 import imread, imwrite # for color detection
    #* user-defined
sys.path.append("../")
from PY.helper import colorDetector

@@

# Load gop image to read
img = imread("../assets/img/gop_2022.png")

@@

transformed= imwrite("../../data/temp/study_2/gop_2022_transformed.png", img_transformed) # save transformed image

masked= imwrite("../../data/temp/study_2/gop_2022_detected.png", result) # save masked image
```

::: {#fig-color-detection-example layout-ncol="2"}
![Resized original image](../../data/temp/study_2/gop_2022_transformed.png){#fig-resized}

![Masked](../../data/temp/study_2/gop_2022_detected.png){#fig-masked}
